---
title: "Reproducible Pitch Presentation"
author: "Armin Boonstra"
date: "14 december 2016"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Premiership table 1993

This presentation gives of the Premiership table application.

The user is able to see the progress of the 22 teams that took part in the 1992-1993 season.

## Application options

- The user can select which teams he or she wants to see in the table
- The user is able to select a week number, to see what the table looks like up to that week number

## Data Source

The data is taken from the Premier League website: https://www.premierleague.com/

This was reworked into a csv file and looks like this:

```{r 5, echo = TRUE}
prem <- read.csv('premiership9293.csv', sep=';')
head(prem)
```

## Example of the graph in the application

The graph shows the progress of up to 22 teams in the Premiership for the 1992-1993 season.
The x-axis shows the weeks and the y-axis the number of points gained per team.

```{r cars, echo = FALSE, message = FALSE, warning=FALSE}
library(ggplot2)

prem <- read.csv('premiership9293.csv', sep=';')
g <- ggplot(prem, aes(x=Week, y=Points, colour = Team)) + geom_line()
g <- g + labs(y='Points')
g
```




